\Title

### 2020-02-14 manuscript/manuscript.tex
Improve EQL implementation and add references

@@

\begin{equation}
    V(\mathbf{p}) = \mathbf{A} \mathbf{c}
    \label{eq:linear-problem}
\end{equation}

\noindent where $V(\mathbf{p}$) is a vertical vector containing the measured
values of $V$ on the observation points, $\mathbf{c}$ a vertical vector
containing the $c$ coefficients and $\mathbf{A}$ is the \emph{Jacobian matrix},
whose elements are defined as the Green's function evaluated on each pair of
points $\mathbf{p}$ and $\mathbf{q}$:

@@

It solves equation~\ref{eq:linear-problem} by a least-squares fit, with
the option of adding a zeroth-order Tikhonov \citep{tikhonov} regularization
through a dimensionless \emph{damping} parameter.
This is achieved by scaling the Jacobian matrix so each column has unit
variance.

Define a diagonal matrix $S$, whose elements corresponds to the standard
deviation of each column of the Jacobian matrix $\mathbf{A}$:

\begin{equation}
    \mathbf{S} =
    \begin{bmatrix}
        \sigma_1 & \cdots &0 \\
        \vdots & \ddots & \vdots \\
        0 & \cdots & \sigma_M
    \end{bmatrix}.
\end{equation}

Equation~\ref{eq:linear-problem} can be written as:

\begin{equation}
    V(\mathbf{p})
    =
    \mathbf{A} \mathbf{S}^{-1} \mathbf{S} \mathbf{c}
    =
    \left[
        \mathbf{A} \mathbf{S}^{-1}
    \right]
    \left[
        \mathbf{S} \mathbf{c}
    \right]
    =
    \mathbf{A_s} \mathbf{c_s}
\end{equation}

\noindent where $\mathbf{A_s}$ the scaled Jacobian matrix and $\mathbf{c_s}$ is
a vector containing scaled coefficients.

Now we can define the misfit function as the sum between the data misfit and
the Tikhonov regularization function:

\begin{equation}
    \phi(\mathbf{c'}) =
        \left\lVert V(\mathbf{p}) - \mathbf{A_s}\mathbf{c_s} \right\rVert ^ 2
        + \lambda \left\lVert \mathbf{c_s} \right\rVert ^2,
    \label{eq:misfit}
\end{equation}

\noindent where $\lambda$ is a dimensionless damping parameter.

After solving the least squares problem, we obtain the set of scaled
coefficients $\mathbf{c_s}$ that minimizes equation~\ref{eq:misfit}.
We can get the corresponding coefficients $\mathbf{c}$ by rescaling
$\mathbf{c_s}$:

\begin{equation}
    \mathbf{c} = \mathbf{S}^{-1} \mathbf{c_s}.
\end{equation}

>>>>

% Define inverse symbol with shorter minus
\newcommand{\inv}{^{\text{-}1}}

@@

\begin{equation}
    \mathbf{d} = \mathbf{A} \mathbf{c}
    \label{eq:linear-problem}
\end{equation}

\noindent where $\mathbf{d}$ is a vertical vector containing the measured
values of $V$ on the observation points, $\mathbf{c}$ a vertical vector
containing the $c$ coefficients and $\mathbf{A}$ is the \emph{Jacobian matrix},
whose elements are defined as the Green's function evaluated on each pair of
points $\mathbf{p}$ and $\mathbf{q}$:

@@

It solves equation~\ref{eq:linear-problem} through least squares with
a zeroth-order Tikhonov \citep{tikhonov1977} regularization in order to
stabilize the solution.
It consists in minimizing the misfit function:

\begin{equation}
    \phi(\mathbf{c}) =
        \left\lVert
            \mathbf{d} - \mathbf{A}\mathbf{c}
        \right\rVert ^ 2
        + \lambda_d \left\lVert \mathbf{c} \right\rVert ^2,
    \label{eq:misfit-unscaled}
\end{equation}

\noindent where $\left\lVert \cdot \right\rVert ^ 2$ symbolizes the L$_2$ norm
and $\lambda_d$ is a \emph{damping} parameter that has the same dimension as
the Jacobian matrix elements.

In order to simplify the choice of this parameter we scale the Jacobian matrix
so each column has unit variance.
We define a diagonal matrix $\mathbf{S}$, whose elements corresponds to the
standard deviation of each column of the Jacobian matrix $\mathbf{A}$:

\begin{equation}
    \mathbf{S} =
    \begin{bmatrix}
        \sigma_1 & \cdots &0 \\
        \vdots & \ddots & \vdots \\
        0 & \cdots & \sigma_M
    \end{bmatrix}
    ,
\end{equation}

\noindent so equation~\ref{eq:linear-problem} can be written as:

\begin{equation}
    \mathbf{d}
    =
    \mathbf{A} \mathbf{S}\inv \mathbf{S} \mathbf{c}
    =
    \left[
        \mathbf{A} \mathbf{S}\inv
    \right]
    \left[
        \mathbf{S} \mathbf{c}
    \right]
    =
    \hat{\mathbf{A}} \hat{\mathbf{c}}
\end{equation}

\noindent where $\hat{\mathbf{A}}$ is the scaled Jacobian matrix and
$\hat{\mathbf{c}}$ is a vector containing scaled coefficients.

The misfit function defined on equation~\ref{eq:misfit-unscaled} can be then
rewritten as follows:

\begin{equation}
    \phi(\hat{\mathbf{c}}) =
        \left\lVert \mathbf{d}
        - \hat{\mathbf{A}}\hat{\mathbf{c}} \right\rVert ^ 2
        + \lambda \left\lVert \hat{\mathbf{c}} \right\rVert ^2,
    \label{eq:misfit}
\end{equation}

\noindent where now $\lambda$ is a \emph{dimensionless} damping parameter.

Misfit function from equation~\ref{eq:misfit} is solved through least squares.
If the number of observation points is equal or larger to the number of
sources, then the linear problem defined on equation~\ref{eq:linear-problem} is
well- or over-determined, respectively. Therefore, the scaled coefficients that
minimize the misfit function can be obtained through \citep{menke1989}:

\begin{equation}
    \hat{\mathbf{c}}_\text{est} =
        \left[
            \hat{\mathbf{A}}^\text{T} \hat{\mathbf{A}}
            + \lambda^2 \mathbf{I}
        \right]\inv
        \hat{\mathbf{A}}^\text{T}
        \mathbf{d}.
\end{equation}

On the other hand, if there are more sources than observation points, the
problem is under-determined and the scaled coefficients can be obtained as
\citep{menke1989}:

\begin{equation}
    \hat{\mathbf{c}}_\text{est} =
    \hat{\mathbf{A}}^\text{T}
        \left[
            \hat{\mathbf{A}} \hat{\mathbf{A}}^\text{T}
            + \lambda^2 \mathbf{I}
        \right]\inv
        \mathbf{d}.
\end{equation}

Once the scaled coefficients are obtained, the sources coefficients
$\mathbf{c}_\text{est}$ can be obtained by rescaling
$\hat{\mathbf{c}}_\text{est}$:

\begin{equation}
    \mathbf{c}_\text{est} = \mathbf{S}\inv \hat{\mathbf{c}}_\text{est}.
\end{equation}
